---
title: "Dynamic Alt-text Options"
format: html
editor: visual
execute:
  warning: false
  echo: fenced
---

```{r libraries}
library(tidyverse)
library(quarto)
library(knitr)
```

::: panel-tabset
## html

### Testing !expr in code chunk settings

#### Using general expressions in fig-alt

Does not work. Image renders but when you check in `developer tools` or right-click image and click on `Inspect`, the alt-text is the code verbatim. It does not evaluate the expressions.

```{r}
#| label: fig-plot
#| fig-cap: "Penguin plot"
#| fig-alt: !expr paste("Scatterplot showing", nrow(palmerpenguins::penguins), "penguins."))
#| output: asis

ggplot(palmerpenguins::penguins, aes(x = flipper_length_mm, y = bill_length_mm)) +
  geom_point()
```

#### Using ggplot2::get_alt_text()

Works! when function is embedded in fig-alt setting.

```{r}
#| label: fig-plot-ggplot2-alt
#| fig-alt: !expr ggplot2::get_alt_text(g)

g <- ggplot(palmerpenguins::penguins, aes(x = flipper_length_mm, y = bill_length_mm)) +
  geom_point() +
  labs(alt = paste("Scatterplot showing", nrow(palmerpenguins::penguins), "penguins."))

g
```

### Static images

I'm not able to render an image with an absolute image path using `knitr::include_graphics()`.

```{r vars setup}

img_path <- "Y:/VISION 2050/Data/Displacement/Displacement Index 2026/docs/Figures/Histograms"
img_fnames <- list.files(img_path, full.names = TRUE)[1:3]
img_alttext <- c("hist01", "hist02", "hist03")

```

Using `include_graphics()` with hardcoded fig-alt text works, but not with `!expr` and a variable.

```{r}
#| fig-alt: !expr img_alttext[1]

include_graphics(img_fnames[1])
```

The following code is not reliable. The image doesn't render. This: `img_fnames[1]` becomes this: `![](%60r%20img_fnames%5B1%5D%60){fig-alt=`r img_alttext[1]`}`

```{r}
#| eval: false

# ![](`r img_fnames[1]`){fig-alt=`r img_alttext[1]`}

```

![](%60r%20img_fnames%5B1%5D%60){fig-alt=`r img_alttext[1]`}

## Resources

Some say that relative paths are required for quarto projects, but that poses a problem when images are used across multiple projects.

- https://github.com/quarto-dev/quarto-cli/issues/12041

:::

