---
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)

```

## Indicator 01 - People of Color

From ACS table B03002, we can estimate the percentage of population that is a race other than non-Hispanic White (per_minority) by tract. The table has estimates and margin of errors for the following indicators:

- Total number of people by tract (pop)
- Total number of Hispanic White people by tract (hw)
- Total number of non-Hispanic White people by tact (nhw)
- Total number of Hispanic people by tract (h)
- Total number of non-Hispanic people by tract (nh)

With these values, the percentage of people that is a race other than non-Hispanic White (per_minority) by tract is estimated as:

```{r, results='asis'}
img_path <- "Y:/VISION 2050/Data/Displacement/Displacement Index 2026/docs/Figures/Histograms"
img_fnames <- list.files(img_path, full.names = TRUE)[1:3]
img_alttext <- c("hist01", "hist02", "hist03")
```

**Insert Summary Table - Indicator 01 here**

```{r pressure, out.width="100%", fig.alt=img_alttext[1],  results='asis'}
knitr::include_graphics(img_fnames[1])
```

